---
title: "Second Hand Vehicle Market in India"
output: html_notebook
---

## Research Question 

Since I came to Penn State, I have learned a lot about other countries. However, I feel like I still haven't learned anything about India yet. Therefore, combining with my interest in cars, I decided to analyze some second hand vehicle market data from India.  

+ What are the factors that are affecting the selling price of used cars in India?
+ Are cars with automatic transmission generally more expensive than cars with manual transmission?(in my theory automatic transmission should be more expensive)
+ Is the data from Indian market same as the US market? 

```{r,warning=FALSE,message=FALSE}
rm(list=ls())
library(readr)
library(DataComputing)
library(tidyverse)
library(party)
library(rpart)
library(rpart.plot)
```
## Data Access
```{r,warning=FALSE,message=FALSE}
CAR <- read_csv("CAR DETAILS FROM CAR DEKHO.csv")
vehicles <- read_csv("vehicles.csv")
```
## Inspecting the initial data
```{r,warning=FALSE,message=FALSE}
head(CAR,message=FALSE)
head(vehicles,message=FALSE)
```
```{r,warning=FALSE,message=FALSE} 
nrow(CAR)
nrow(vehicles)
ncol(CAR)
ncol(vehicles)
```

8 variables and 4340 observations in CAR table, 25 variables and 423857 observations in vehicles table. 

## Data Wrangling
```{r,warning=FALSE,message=FALSE}
Without_Name_IN <- # data wrangling the table for used car market data from India
  CAR %>%
  group_by(km_driven,fuel,transmission) %>% # factors that I would like to explore with graph 
  summarise(price=mean(selling_price), total=n())%>%
  spread(key=fuel, value=total, fill=0) %>% # spread the fuel category to make the comparison more effective
  rename(diesel=Diesel, electric=Electric, Transmission=transmission) %>% # so that two tables can match 
  mutate(country="India") # identify the country

Without_Name_IN$transmission=tolower(Without_Name_IN$Transmission)# in order to later match with the US data  

Without_Name_IN
```

```{r,warning=FALSE,message=FALSE}
Without_Name_US <- # data wrangling the table for used car market data from US
  vehicles %>%
  filter(!is.na(price),!is.na(transmission),!is.na(fuel),!is.na(odometer),odometer != 0) %>% # filter our the NA values and new cars (since we are comparing the used cars)
  mutate(km_driven=odometer) %>% # match the variable name from India 
  group_by(km_driven,price,transmission,fuel) %>%
  summarise(total=n()) %>%
   spread(key=fuel, value=total, fill=0)%>%
  mutate(country="America")

Without_Name_US
```
```{r,warning=FALSE,message=FALSE}
Combined_Table <-
  Without_Name_IN %>%
  mutate(price=price*0.014)%>% #change currency unit to usd
 full_join(Without_Name_US)


Combined_Table
```
```{r,warning=FALSE,message=FALSE}
logfit<- lm(log(selling_price)~transmission+year+km_driven+fuel+seller_type+owner, data = CAR) # try to figure out the relationship between selling price and other variables. Log transformation is applied in order to met the model assumptions
summary(logfit)
plot(logfit) # check the model assumption 
```
```{r,warning=FALSE,message=FALSE}
treemod <- rpart(selling_price~transmission+year+fuel+km_driven, data=CAR)
prp(treemod)
```
Key Takeaways from the table

+ Transmission type, fuel type, number of previous owners, seller type, year of the car, and km_driven are significant predictors of selling price for the used car in Indian market. 
+ Each condition of the car can lead to different price. 

# Data Visualization 
```{r,warning=FALSE,message=FALSE}
CAR %>%
  ggplot(aes(x=km_driven, y=selling_price, fill=transmission)) +
  facet_wrap(fuel~.) +
  geom_point(aes(color=transmission), alpha=0.6)+
  geom_boxplot(alpha=0.3)+
  ylab("price") + 
  xlim(0,350000)+ # majority of cars have millage bellow 350000, in order to reduce the effect of outliers, the max is set to 350000. 
  ylim(0,3000000)# majority of cars have selling price bellow 3000000, in order to reduce the effect of outliers, the max is set to 3000000. 
```
+ Auto transmission is predominantly in the diesel and petrol category while manual is existing in all categories except electric. 
+ There is a negative linear relationship between millage and selling price in all fuel types. 

```{r,warning=FALSE,message=FALSE}
vehicles %>%
  filter(!is.na(price),!is.na(transmission),!is.na(fuel),!is.na(odometer),odometer != 0) %>%
  ggplot(aes(x=odometer,y=price,fill=transmission)) +
  facet_wrap(fuel~.) +
  geom_point(aes(color=transmission),alpha=0.6)+
  geom_boxplot(alpha=0.3)+ 
  xlab("km_driven") +
  xlim(0,350000)+
  ylim(0,300000)
```
+ All fuel types have three kinds of transmissions, the difference in the medial price among three transmissions is small. 
+ There is a negative linear relationship between millage and selling price in all fuel types.

```{r,warning=FALSE,message=FALSE}
Combined_Table %>%
  ggplot(aes(x=km_driven,y=price,fill=transmission)) +
  geom_point(aes(color=transmission),alpha=0.6)+
  geom_boxplot(alpha=0.5)+
  xlim(0,350000)+
  ylim(0,300000)
```
+ The plot is about the combined table for both India and America. From the graph, there is a negative linear relationship between millage and selling price.
+ The auto transmission still has slightly higher median price than manual transmission even though the have similar range. 

```{r,warning=FALSE,message=FALSE}
Combined_Table %>%
  ggplot(aes(x=km_driven,y=price,fill=transmission)) +
  geom_point(aes(color=transmission),alpha=0.6)+
  geom_boxplot(alpha=0.5)+
  facet_wrap(country~.)+
  xlim(0,350000)+
  ylim(0,300000)
```
+ In India, the median selling price for auto transmission is much higher than manual transmission. Auto transmission also have wider price range. 
+ In America, the difference in median selling price between auto and manual transmission is not obvious. However, since there is a "other" type of transmission, after research, still belongs to the broader category of auto transmission. Therefore, auto transmission still have higher median selling price. 

## Challenge 
+ My biggest challenge is when trying to combine two tables, the India table has capital cased transmission (Automatic/Manual) while the US table has lower cased (automatic/manual). In order to effectively compare two data sets, I took hours of work to figure this way - lower case the entire column instead of matching. I also had to rename some of my variables so that R would treat those as same category. 

## Key Takeaway
+ According to the data from India, since the p-value is less than 0.05, we can conclude that transmission, fuel, km_driven, year, seller type, and number of owners are significant predictors of selling price in the India market. 
+ For India market, the selling price for auto transmission is significantly higher than manual transmission. 
+ In comparison, the selling price for auto transmission and manual transmission are about the same in the US. 
+ The Indian market favors automatic transmission while the Us market is indifferent. 

## Github repo
[Click here](https://sihan-wu.github.io/Fianl-Proj/) 
