---
title: "Second Hand Vehicle Market in India"
output: html_notebook
---

## Research Question 

Since I came to Penn State, I have learned a lot about countries. However, I feel like I still haven't learned anything about India yet. Therefore, I decided to analysis some second hand vehicle market data in India.  
+ What are the factors that are affecting the selling price of used cars in India?
+ Are cars with automatic transmission generally more expensive than cars with manual transmission?(in my theory automatic transmission should be more expensive)
+ Is the data from Indian market same as the US market? 

```{r,warning=FALSE,message=FALSE}
rm(list=ls())
library(readr)
library(DataComputing)
library(tidyverse)
library(party)
```
## Data Access
```{r,warning=FALSE,message=FALSE}
CAR <- read_csv("CAR DETAILS FROM CAR DEKHO.csv")
vehicles <- read_csv("vehicles.csv")
```
## Inspecting the initial data
```{r,warning=FALSE,message=FALSE}
head(CAR,message=FALSE)
head(vehicles,message=FALSE)
```
```{r,warning=FALSE,message=FALSE} 
nrow(CAR)
nrow(vehicles)
ncol(CAR)
ncol(vehicles)
```
## Data Wrangling
```{r,warning=FALSE,message=FALSE}
Without_Name_IN <-
  CAR %>%
  group_by(km_driven,fuel,transmission) %>%
  summarise(price =mean(selling_price), total=n())%>%
  spread(key=fuel, value=total, fill=0) %>%
  rename(diesel=Diesel, electric=Electric, Transmission=transmission) %>% # so that two tables can match 
  mutate(country="India")

Without_Name_IN$transmission=tolower(Without_Name_IN$Transmission)# My biggest challenge! 

Without_Name_IN
```

```{r,warning=FALSE,message=FALSE}
Without_Name_US <-
  vehicles %>%
  filter(!is.na(price),!is.na(transmission),!is.na(fuel),!is.na(odometer),odometer != 0) %>%
  mutate(km_driven=odometer) %>%
  group_by(km_driven,price,transmission,fuel) %>%
  summarise(total=n()) %>%
   spread(key=fuel, value=total, fill=0)%>%
  mutate(country="America")

Without_Name_US
```
```{r,warning=FALSE,message=FALSE}
Combined_Table <-
  Without_Name_IN %>%
  mutate(price=price*0.014)%>% #change currency unit to usd
 full_join(Without_Name_US)


Combined_Table
```
```{r,warning=FALSE,message=FALSE}
logfit<- lm(log(selling_price)~transmission+year+km_driven+fuel+seller_type+owner, data = CAR) # try to figure out the relationship betwen selling price and other variables 
summary(logfit)
plot(logfit) # check the model assumption 
```
#Data Visualization 
```{r,warning=FALSE,message=FALSE}
CAR %>%
  ggplot(aes(x=km_driven, y=selling_price, fill=transmission)) +
  facet_wrap(fuel~.) +
  geom_point(aes(color=transmission), alpha=0.6)+
  geom_boxplot(alpha=0.3)+
  xlim(0,350000)+
  ylim(0,3000000)
```
```{r,warning=FALSE,message=FALSE}
vehicles %>%
  filter(!is.na(price),!is.na(transmission),!is.na(fuel),!is.na(odometer),odometer != 0) %>%
  ggplot(aes(x=odometer,y=price,fill=transmission),xlab="km_driven",ylab="selling_price") +
  facet_wrap(fuel~.) +
  geom_point(aes(color=transmission),alpha=0.6)+
  geom_boxplot(alpha=0.3)+
  xlim(0,350000)+
  ylim(0,300000)
```
```{r,warning=FALSE,message=FALSE}
Combined_Table %>%
  ggplot(aes(x=km_driven,y=price,fill=transmission)) +
  geom_point(aes(color=transmission),alpha=0.6)+
  geom_boxplot(alpha=0.5)+
  facet_wrap(country~.)+
  xlim(0,350000)+
  ylim(0,300000)

#This graph will show a direct comparison between 
```
## Challenge 
+ My biggest challenge! When trying to combine two tables, the India table has capital cased transmission (Automatic/Manual) while the US table has lower cased (automatic/manual). In order to effectively compare two data sets, I took hours of work to figure this way - lower case the entire column instead of matching

## Key Takeaway
+ According to the data from India, since the p-value is less than 0.05, we can conclude that transmission, fuel, km_driven, year, seller type, and number of owners are significant predictors of selling price in the India market. 
+ For India market, the selling price for auto transmission is significantly higher than manual transmission. 
+ In comparison, the selling price for auto transmission and manual transmission are about the same in the US. 
+ The Indian market favors automatic transmission while the Us market is indifferent. 
